---
title: "Data Science With R - Part 02"
author: "Edneide Ramalho"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: 
    html_document:
      highlight: textmate
      logo: logo.png
      theme: jou
      number_sections: yes
      toc: yes
      toc_float:
        collapsed: yes
        smooth_scroll: no
      df_print: paged
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Imports

```{r}
library(tidyverse)
library(janitor)
library(readr)
library(gtsummary)
library(summarytools)
library(kableExtra)
library(knitr)
library(gridExtra)
library(summarytools)
library(randomForest)
library(reshape2)
library(tidymodels)
```

# Helper Functions

```{r functions}
# Top @K precision and recall function ---------
metrics_at_k_function <- function(model_results, k){
  df_results <- model_results %>% 
  arrange(desc(.pred_yes)) %>% 
  mutate(
    TP = ifelse(.pred_class == "yes" & response == "yes", 1, 0),
    FP = ifelse(.pred_class == "yes" & response == "no", 1, 0),
    FN = ifelse(.pred_class == "no" & response == "yes", 1, 0),
    TN = ifelse(.pred_class == "no" & response == "no", 1, 0)
  ) 
  
  # Create list for precision and recall
  precision_at_k <- list()
  recall_at_k <- list()

  # Populate the metric list
  for (i in 1:k) {
    subset_k <- df_results %>% 
    dplyr_row_slice(1:i)
    
    precision_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FP %>% sum())
  
    recall_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FN %>% sum())
}

    metrics_at_k <- df_results %>% 
  dplyr_row_slice(1:k) %>% 
  mutate(
    precision_at_k = unlist(precision_at_k),
    recall_at_k = unlist(recall_at_k)
  )
    
 return(metrics_at_k)
}

# Final metrics @K Function ----------------------
final_metrics_at_k <- function(model_results, k){
  
  model_metrics_at_k <- metrics_at_k_function(model_results, k)

  model_metrics_at_k %>% 
    slice(k) %>% 
    select(precision_at_k, recall_at_k)
}
```

# Data

```{r}
df <- readRDS("df_cleaned.rds")

selected_columns <- c(
  "id", 
  "age",
  "vehicle_damage",
  "days_associated",
  "previously_insured",
  "health_annual_paid", 
  "policy_sales_channel", 
  "region_code",
  "response"
)

# Final dataset
df_selected <- df %>% 
  select(all_of(selected_columns)) 

saveRDS(df_selected, "df_selected.rds")
```

# Pre-processing

```{r}
region_encoder <- readRDS("region_encoder.rds")
policy_encoder <- readRDS("policy_encoder.rds")

# Create function
encoder_function <- function(df){
  df %>% 
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% 
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num) 
}
```

```{r}
df_selected <- encoder_function(df_selected)
```

## Split into train and test datasets

```{r}
set.seed(123)

df_split <- df_selected %>% 
  initial_split(prop = 0.80, strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()

# Taking a look on the datasets
df_train
df_test
```

## Applying steps

```{r}
df_recipe <- recipe(response ~ .,
       data = df_train %>% select(-id)) %>% 
  step_normalize(age, days_associated) %>% 
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

```{r}
# Train the recipe
df_prep <- df_recipe %>% 
  prep(training = df_train)

df_train_preprocessed <- df_prep %>% 
  bake(new_data = df_train)

df_test_preprocessed <- df_prep %>% 
  bake(new_data = df_test)
```

# 💻 Logistic Regression

```{r logistic_regression}
# Model Specification -----------
logistic_model <- logistic_reg() %>% 
  set_engine('glm') %>% 
  set_mode('classification')
```

```{r, eval=FALSE}
# Model Fitting -----------
start_time <- Sys.time()

logistic_fit <- logistic_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(logistic_fit, "logistic_fit.rds")
```

```{r}
logistic_fit <- readRDS("logistic_fit.rds")

# Prediction ----------
class_preds <- logistic_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')

prob_preds <- logistic_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
lr_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_lr <-  conf_mat(
  lr_results, truth = response, estimate = .pred_class
)
```

```{r}
# Calculating metrics @K
lr_final_at_k_metrics <- tibble(
  model = "Logistic Regression"
) %>% 
  bind_cols(final_metrics_at_k(lr_results, 2000))

lr_final_at_k_metrics
```

## Gain & Lift Curves

```{r}
# Gain curve
gain_curve(lr_results, response, .pred_yes) %>% 
  autoplot()
```

```{r}
# Lift curve
lift_curve(lr_results, response, .pred_yes) %>% 
  autoplot()
```

Gain: By approaching 25% of the ordered list , \~ 60% of all interested clients are reached.

Lift: By approaching 25% of the ordered list , the model performed \~2.3 times better than a random list.

# Decision Tree 💻

Time to fit the model: 1.065924 secs.

```{r, eval=FALSE}
# Model Specification -----------
dt_model <- decision_tree(tree_depth = 10) %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

# Model Fitting -----------
start_time <- Sys.time()

dt_fit <- dt_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(dt_fit, "dt_fit.rds")

```

```{r}
dt_fit <- readRDS("dt_fit.rds")

# Prediction ----------
class_preds <- dt_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')

prob_preds <- dt_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
dt_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_dt <-  conf_mat(
  dt_results, truth = response, estimate = .pred_class
)
```

```{r}
# Calculating metrics @K
dt_final_at_k_metrics <- tibble(
  model = "Decision tree"
) %>% 
  bind_cols(final_metrics_at_k(dt_results, 2000))

dt_final_at_k_metrics
```

```{r}
# Gain and Lift Curves
gain_curve(dt_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(dt_results, response, .pred_yes) %>% 
  autoplot()
```

```{r}
dt_results %>% 
  select(.pred_yes, .pred_no) %>% 
  summary()
```

As the probabilities are constant throughout the rows there is no way to calculate gain and lift. So, this is not a good model to rank our clients.

# Random Forest 💻

Time to run the model: 8.450113 mins

```{r, eval=FALSE}
# Model Specification -----------
rf_model <- rand_forest(
  mtry = 3,
  trees = 1000,
  min_n = 100
  ) %>% 
  set_engine('ranger') %>% 
  set_mode('classification')

# Model Fitting -----------
start_time <- Sys.time()

rf_fit <- rf_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(rf_fit, "rf_fit.rds")
```

```{r}
rf_fit <- readRDS("rf_fit.rds")

# Prediction ----------
class_preds <- rf_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')

prob_preds <- rf_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
rf_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_rf <-  conf_mat(
  rf_results, truth = response, estimate = .pred_class
)
```

```{r}
# Calculating metrics @K
rf_final_at_k_metrics <- tibble(
  model = "Random Forest"
) %>% 
  bind_cols(final_metrics_at_k(rf_results, 2000))

rf_final_at_k_metrics
```

```{r}
# Gain and Lift Curves
gain_curve(rf_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(rf_results, response, .pred_yes) %>% 
  autoplot()
```

Gain: By approaching 25% of the ordered list , \~ 64% of all interested clients are reached.

Lift: By approaching 25% of the ordered list , the model performed \~2.3 times better than a random list.

# XGBoost 💻

Time to train the model: 5.701178 mins.

```{r, eval=FALSE}
# Model Specification -----------
xgb_model <- boost_tree(
  mtry = 6,
  trees = 1000,
  min_n = 28,
  tree_depth = 14,
  loss_reduction = 0.01,
  sample_size = 0.27,
  ) %>% 
  set_engine('xgboost') %>% 
  set_mode('classification')

# Model Fitting -----------
start_time <- Sys.time()

xgb_fit <- xgb_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(xgb_fit, "xgb_fit.rds")
```

```{r}
xgb_fit <- readRDS("xgb_fit.rds")

# Prediction ----------
class_preds <- xgb_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')

prob_preds <- xgb_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')

# Combine results -----------
xgb_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

# Confusion Matrix ------------
confusion_matrix_xgb <-  conf_mat(
  xgb_results, truth = response, estimate = .pred_class
)
```

```{r}
# Calculating metrics @K
xgb_final_at_k_metrics <- tibble(
  model = "XGBoost"
) %>% 
  bind_cols(final_metrics_at_k(xgb_results, 2000))

xgb_final_at_k_metrics
```

```{r}
# Gain and Lift Curves
gain_curve(xgb_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(xgb_results, response, .pred_yes) %>% 
  autoplot()
```

Gain: By approaching 25% of the ordered list, \~ 62% of all interested clients are reached.

Lift: By approaching 25% of the ordered list, the model performed \~2.4 times better than a random list.

# KNN 💻

Time to train the model: 19.01394 mins

Time for prediction: 9.316501 mins

```{r, eval=FALSE}
library(kknn)

# Model Specification -----------
knn_model <- nearest_neighbor(weight_func = "rectangular",
                              neighbors = 3) %>% 
  set_engine('kknn') %>% 
  set_mode('classification')

# Model Fitting -----------
start_time <- Sys.time()

knn_fit <- knn_model %>% 
  fit(response ~., 
      data = df_train_preprocessed)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(knn_fit, "knn_fit.rds")
```

```{r, eval=FALSE}
knn_fit <- readRDS("knn_fit.rds")

start_time <- Sys.time()
# Prediction ----------
class_preds <- knn_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'class')

prob_preds <- knn_fit %>% 
  predict(new_data = df_test_preprocessed,
          type = 'prob')
end_time <- Sys.time()

print(end_time - start_time)

# Combine results -----------
knn_results <- df_test %>% 
  select(id, response) %>% 
  bind_cols(class_preds, prob_preds)

saveRDS(knn_results, "knn_results.rds") 
```

```{r}
knn_results <- readRDS("knn_results.rds")

# Confusion Matrix ------------
confusion_matrix_knn <-  conf_mat(
  knn_results, truth = response, estimate = .pred_class
)

# Calculating metrics @K
knn_final_at_k_metrics <- tibble(
  model = "KNN"
) %>% 
  bind_cols(final_metrics_at_k(knn_results, 2000))

knn_final_at_k_metrics
```

```{r}
# Gain and Lift Curves
gain_curve(knn_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(knn_results, response, .pred_yes) %>% 
  autoplot()
```

Gain: By approaching 25% of the ordered list, \~ 62% of all interested clients are reached.

Lift: By approaching 25% of the ordered list, the model performed \~2.2 times better than a random list.

# Model Comparison

```{r}
rf_final_at_k_metrics %>% 
  bind_rows(dt_final_at_k_metrics, 
            lr_final_at_k_metrics,
            xgb_final_at_k_metrics,
            knn_final_at_k_metrics) %>% 
  arrange(desc(recall_at_k))

```
