---
title: "Health Insurance Cross Sell - Part 03"
author: "Edneide Ramalho"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output: 
    html_document:
      highlight: textmate
      logo: logo.png
      theme: jou
      number_sections: yes
      toc: yes
      toc_float:
        collapsed: yes
        smooth_scroll: no
      df_print: paged
      code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Imports

```{r}
library(tidyverse)
library(janitor)
library(readr)
library(gtsummary)
library(summarytools)
library(kableExtra)
library(knitr)
library(gridExtra)
library(summarytools)
library(randomForest)
library(reshape2)
library(tidymodels)
```

# Helper Functions

```{r functions}
# Encoding
region_encoder <- readRDS("region_encoder.rds")
policy_encoder <- readRDS("policy_encoder.rds")

# Create function
encoder_function <- function(df){
  df %>% 
  left_join(region_encoder) %>% 
  select(-region_code) %>% 
  rename(region_code = region_num) %>% 
  left_join(policy_encoder) %>% 
  select(-policy_sales_channel) %>% 
  rename(policy_sales_channel = policy_num) 
}

# Top @K precision and recall function ---------
metrics_at_k_function <- function(model_results, k){
  df_results <- model_results %>% 
  arrange(desc(.pred_yes)) %>% 
  mutate(
    TP = ifelse(.pred_class == "yes" & response == "yes", 1, 0),
    FP = ifelse(.pred_class == "yes" & response == "no", 1, 0),
    FN = ifelse(.pred_class == "no" & response == "yes", 1, 0),
    TN = ifelse(.pred_class == "no" & response == "no", 1, 0)
  ) 
  
  # Create list for precision and recall
  precision_at_k <- list()
  recall_at_k <- list()

  # Populate the metric list
  for (i in 1:k) {
    subset_k <- df_results %>% 
    dplyr_row_slice(1:i)
    
    precision_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FP %>% sum())
  
    recall_at_k[[i]] <- (subset_k$TP %>% sum())/(subset_k$TP %>% sum() + subset_k$FN %>% sum())
}

    metrics_at_k <- df_results %>% 
  dplyr_row_slice(1:k) %>% 
  mutate(
    precision_at_k = unlist(precision_at_k),
    recall_at_k = unlist(recall_at_k)
  )
    
 return(metrics_at_k)
}

# Final metrics @K Function ----------------------
final_metrics_at_k <- function(model_results, k){
  
  model_metrics_at_k <- metrics_at_k_function(model_results, k)

  model_metrics_at_k %>% 
    slice(k) %>% 
    select(precision_at_k, recall_at_k)
}
```

# Data

```{r}
df <- readRDS("df_cleaned.rds")

selected_columns <- c(
  "id", 
  "age",
  "vehicle_damage",
  "days_associated",
  "previously_insured",
  "health_annual_paid", 
  "policy_sales_channel", 
  "region_code",
  "response"
)

# Final dataset
df_selected <- df %>% 
  select(all_of(selected_columns)) 

saveRDS(df_selected, "df_selected.rds")
```

# Pre-processing

```{r}
df_selected.rds <- readRDS("df_selected.rds")
df_selected <- encoder_function(df_selected)
```

# Splitting into train and test data sets

```{r}
set.seed(123)

df_split <- df_selected %>% 
  initial_split(prop = 0.80, strata = response)

df_train <- df_split %>% 
  training()

df_test <- df_split %>% 
  testing()
```

```{r}
df_recipe <- recipe(response ~ .,
       data = df_train %>% select(-id)) %>% 
  step_normalize(age, days_associated) %>% 
  step_scale(health_annual_paid) %>% 
  step_dummy(all_nominal(), -all_outcomes())
```

# Kfold cross validation

```{r}
df_kfolds <- vfold_cv(df_train %>% select(-id),
                      v = 5, strata = response)
```

# Logistic Regression 💻

```{r}
# Model specification
lr_model <- logistic_reg(
  penalty = tune(),
  mixture = tune()
) %>% 
  set_engine('glmnet') %>% 
  set_mode('classification')

hardhat::extract_parameter_set_dials(lr_model)
```

```{r}
# Creating the grid
lr_grid <- grid_regular(extract_parameter_set_dials(lr_model),
                        levels = 5)
```

```{r, eval = FALSE}
library(glmnet)

doParallel::registerDoParallel()

start_time <- Sys.time()

# Tune the model
lr_tune <- tune_grid(
  lr_model, df_recipe,
  resamples = df_kfolds,
  grid = lr_grid
)


end_time <- Sys.time()

print(end_time - start_time )

saveRDS(lr_tune, "lr_tune.rds")
```

```{r}
lr_tune <- readRDS("lr_tune.rds")

# Select the best hyperparameters
lr_param <- lr_tune %>% 
  select_best("roc_auc")

# Apply the best hyperparameters to the model
tidy_lr_model <- finalize_model(lr_model, lr_param)

# Create workflow
lr_wkfl <- workflow() %>% 
  add_model(tidy_lr_model) %>% 
  add_recipe(df_recipe)
```

```{r, eval=FALSE}
# Train final model
doParallel::registerDoParallel()

start_time <- Sys.time()

# Train the model
lr_res <- last_fit(lr_wkfl, df_split)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(lr_res, "lr_res.rds")
```

```{r}
lr_res <- readRDS("lr_res.rds")

# Confusion matrix
lr_res %>% 
  unnest(.predictions) %>% 
  conf_mat(truth = response, estimate = .pred_class)
  
```

```{r}
lr_results <- lr_res %>% 
  unnest(.predictions) %>% 
  select(.pred_yes:response)

# Metrics @K
lr_metrics_at_k <- final_metrics_at_k(lr_results, 2000)
lr_metrics_at_k <- tibble(model = "Logistic Regression") %>% 
  bind_cols(lr_metrics_at_k)
lr_metrics_at_k
```

```{r}
# Gain and Lift Curves
gain_curve(lr_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(lr_results, response, .pred_yes) %>% 
  autoplot()
```

Gain:By approaching 25% of the ordered list, \~ 61% of all interested clients are reached.

Lift: By approaching 25% of the ordered list, the model performs \~ 2.3 times better than the random list.

# Decision Tree 💻

```{r}
# Model specification ----------------
tree_model <- decision_tree(
  cost_complexity = tune(),
  min_n = tune(),
  tree_depth = tune()
) %>% 
  set_engine('rpart') %>% 
  set_mode('classification')

hardhat::extract_parameter_set_dials(tree_model)

# Creating the grid
tree_grid <- grid_regular(extract_parameter_set_dials(tree_model),
                        levels = 3)
```

```{r, eval = FALSE}
# Tune the model ------------
doParallel::registerDoParallel()
start_time <- Sys.time()

tree_tune <- tune_grid(
  tree_model, df_recipe,
  resamples = df_kfolds,
  grid = tree_grid
)

end_time <- Sys.time()

print(end_time - start_time )
saveRDS(tree_tune, "tree_tune.rds")
```

```{r}
tree_tune <- readRDS("tree_tune.rds")

# Select the best hyperparameters ---------------
tree_param <- tree_tune %>% 
  select_best("roc_auc")

# Apply the best hyperparameters to the model ----------
tidy_tree_model <- finalize_model(tree_model, tree_param)

# Create workflow ---------------
tree_wkfl <- workflow() %>% 
  add_model(tidy_tree_model) %>% 
  add_recipe(df_recipe)
```

```{r, eval=FALSE}
# Train final model -----------------
doParallel::registerDoParallel()
start_time <- Sys.time()

tree_res <- last_fit(tree_wkfl, df_split)

end_time <- Sys.time()

print(end_time - start_time)

saveRDS(tree_res, "tree_res.rds")
```

```{r}
# Confusion matrix -----------------
tree_res <- readRDS("tree_res.rds")

tree_conf_mat <- tree_res %>% 
  unnest(.predictions) %>% 
  conf_mat(truth = response, estimate = .pred_class)

# Results - data frame ---------
tree_results <- tree_res %>% 
  unnest(.predictions) %>% 
  select(.pred_yes:response)

# Metrics @K -------------------
tree_metrics_at_k <- final_metrics_at_k(tree_results, 2000)
tree_metrics_at_k <- tibble(model = "Decision Tree") %>% 
  bind_cols(tree_metrics_at_k)
tree_metrics_at_k

# Gain and Lift Curves --------------------
gain_curve(tree_results, response, .pred_yes) %>% 
  autoplot()

lift_curve(tree_results, response, .pred_yes) %>% 
  autoplot()
```

Gain:By approaching 25% of the ordered list, \~ 62% of all interested clients are reached.

Lift: By approaching 25% of the ordered list, the model performs \~ 2.6 times better than the random list.




# Model Comparison
```{r}
models_df <- bind_rows(
  lr_metrics_at_k,
  tree_metrics_at_k
)
models_df
```

